Structuring Theories with Implicit Morphisms

### 2018-10-14 appl.tex
update

With implicit morphisms, we can solve this problem by making only the following local changes:
\begin{compactenum}
  \item We rename $s$ to $s'$.
  \item We delete the declaration $n:E$ from $s'$.
  \item We create new theories $r'=\{\icl{r},\,D\}$ and $s=\{\icl{s'},D\}$.
  \item We change $t$ to $t=\{\icl{r'},\icl{s'}\}$.
  \item We add an implicit morphism $s\to t$ that maps $s?n$ to $r'?n$.
\end{compactenum}
Now $t$ has the desired new structure.
But, all old references to $s?n$ stay well-formed so that no global changes are needed.

\ednote{@DM: maybe make a tikz for the before/after situations}

>>>>

With implicit morphisms, we can solve this problem by making only the following local changes:
\begin{compactenum}
  \item We rename $s$ to $s'$.
  \item We delete the declaration $n:E$ from $s'$.
  \item We create new theories $r'=\{\icl{r},\,D\}$ and $s=\{\icl{s'},D\}$.
  \item We change $t$ to $t=\{\icl{r'},\icl{s'}\}$.
  \item We add an implicit morphism $s\to t$ that maps $s?n$ to $r'?n$.
\end{compactenum}
Now $t$ has the desired new structure.
But, all old references to $s?n$ stay well-formed so that no global changes are needed, as in \autoref{fig:refac}.

\begin{figure}\begin{center}

\begin{minipage}[t]{0.4\textwidth}
\begin{center}
Before:

\begin{tikzpicture}[scale=1.5]
  \node (t) at (0,0) {$t$};
  \node (r) at (-1,-2) {$r$};
  \node (s) at (1,-1) {$s$};
  \draw[right hook-latex] (r) to (t) {};
  \draw[right hook-latex] (s) to (t) {};

  %\node[thy,inner sep=.3cm,fill=gray] (t1) at (0,0) {};
  %\node at (t1.north west) {$S$};
  %\node at (t1) {$D$};
  %\node[thy,inner sep=.5cm,fill=lightgray] (s2) at (2,0) {};
  %\node[thy,inner sep=.3cm,fill=gray] (t2) at (2,0) {};
  %\node at (t2.north west) {$T$};
  %\node at (t2) {$C$};
  %\draw[view] (t1) to[out=10,in=170] node[above] {$\sigma$} (t2);
\end{tikzpicture}
\end{center}
\end{minipage}
\begin{minipage}[t]{0.4\textwidth}
\begin{center}
After:

\begin{tikzpicture}[scale=1.5]
  \node (t) at (0,0) {$t$};
  \node (rp) at (-1,-1) {$r'$};
  \node (s) at (1,-1) {$s$};

  \node (r) at (-1,-2) {$r$};
  \node (sp) at (1,-2) {$s'$};
  \draw[right hook-latex] (r) to (rp) {};
  \draw[right hook-latex] (sp) to (s) {};

  \draw[right hook-latex] (rp) to (t) {};
  \draw[right hook-latex] (sp) to (t) {};

  \draw[arrow] (s) to (t);

  %\node[thy,inner sep=.3cm,fill=gray] (t1) at (0,0) {};
  %\node at (t1.north west) {$S$};
  %\node at (t1) {$D$};
  %\node[thy,inner sep=.5cm,fill=lightgray] (s2) at (2,0) {};
  %\node[thy,inner sep=.3cm,fill=gray] (t2) at (2,0) {};
  %\node at (t2.north west) {$T$};
  %\node at (t2) {$C$};
  %\draw[view] (t1) to[out=10,in=170] node[above] {$\sigma$} (t2);
\end{tikzpicture}
\end{center}
\end{minipage}

\end{center}
\caption{An Example for Transparent Refactoring}\label{fig:refac}
\end{figure}
